Abstractions for Multi-Sorted Substitutions

### 2023-09-16 paper/paper.tex
Update.

  In this paper we present a simplified version of the actual
  framework, focusing on the core concepts. We present all necessary
  definitions and lemmas, but omit some proofs for the sake of
  space. The omitted proofs can be found in Appendix~{TODO} and the
  supplementary material. The full framework can be found at TODO.

@@

  The formal definition of the generic class can be found in
  Appendix~TODO and the actual implementation.

@@

  \clearpage
  \appendix
\end{document}

>>>>

  In this paper we present a simplified version of the actual
  framework, focusing on the core concepts. We present all necessary
  definitions and lemmas, but omit some proofs for the sake of
  space. The omitted proofs can be found in Appendix~\ref{sec:proofs} and the
  supplementary material. The full framework can be found at TODO.

@@

  The formal definition of the generic class can be found in
  Appendix~\ref{sec:generic-class} and the actual implementation.

@@

  \clearpage
  \appendix
  \onecolumn

  \section{Omitted Proofs}
  \label{sec:proofs}

  \subsection{Proofs for Section~\ref{sec:maps}}
  \LibCode\KIdLift
  \LibCode\KIdLiftProof

  % \AppCode\FTraversalId
  % \AppCode\FTraversalIdProofInteresting
  % \LibCode\FTraversalIdProofRest

  \subsection{Proofs for Section~\ref{sec:composition}}
  \LibCode\KComposeKitAp
  \LibCode\KComposeKitApProof

  \LibCode\KDistLiftCompose
  \LibCode\KDistLiftComposeProof

  \LibCode\KCommLiftWeaken
  \LibCode\KCommLiftWeakenProof

  \LibCode\KCommLiftWeakenTraverse
  \LibCode\KCommLiftWeakenTraverseProof

  \LibCode\KWeakenCancelsSingle
  \LibCode\KWeakenCancelsSingleProof

  \LibCode\KWeakenCancelsSingleTraverse
  \LibCode\KWeakenCancelsSingleTraverseProof

  \LibCode\KDistLiftSingle
  \LibCode\KDistLiftSingleProof

  \LibCode\KDistLiftSingleTraverse
  \LibCode\KDistLiftSingleTraverseProof

  % \AppCode\FAssoc
  % \AppCode\FAssocProofInteresting
  % \AppCode\FAssocProofRest

  \subsection{Proofs for Section~\ref{sec:typing}}
  \LibCode\KLiftTyping
  \LibCode\KLiftTypingProof

  \LibCode\KSingleTyping
  \LibCode\KSingleTypingProof

  % \AppCode\FSubjectReduction
  % \AppCode\FSubjectReductionProofInteresting

  \section{Generic Class of Object Languages}
  \label{sec:generic-class}

\end{document}
